How to Analyze Build Logs---A~Comparative Study of Chunk~Retrieval~Techniques

### 2020-04-01 tse-paper/content.tex
describe struc cats

\lstset{
  language=caml,
  morekeywords={StartExtraction, RegexPosition, RegexPair, EndExtraction},
  keywordstyle=\bfseries\color{black},
  escapeinside=//
}
\begin{figure}[!t]
  \centering
  \begin{lstlisting}[breaklines=true]
StartExtraction(RegexPair("Colon/{\color{Plum}$\circ$}/Line Separator", "ALL CAPS")) in EndExtraction(RegexPair("/{\color{Plum}$\varepsilon$}/", "Line Separator/{\color{Plum}$\circ$}/Line Separator"))
  \end{lstlisting}  
  \caption{Simiplified regular expression produced by PBE when trained
  with examples from \Cref{lst:chunk-example-1,lst:chunk-example-2}}
  \label{lst:prose-program-simplified}
\end{figure}

@@

The results of our empirical comparison study on the chunk retrieval techniques
show that the structural representation of the targeted chunk greatly influences
the performance of the chunk retrieval techinques.
\Cref{lst:chunk-example-1,lst:chunk-example-2} show two exemplary log chunks
from Android/Gradle build logs. Both chunks contain the information on why the
corresponding build failed. When PBE is trained on these two examples it produces
a regular expression similar to \Cref{lst:prose-program-simplified}. The retrieval
starts after a colon followed by a line separator and before a capital letter.
It ends before two line separators, consistent with the two example chunks from
\Cref{lst:chunk-example-1,lst:chunk-example-2}.
This shows, that the characters structuring the text around the chunk are cruicial
for regular expressions to identify the targeted log chunk. In fact, if the third
example from \Cref{lst:chunk-example-3} with a different structural representation is added,
PBE is not able to syntesize a program and returns ``\texttt{no program found}''

@@

% TODO: Add structural category explanation
% TODO: Add running example

@@

We recommend PBE for use cases where the desired information is always
represented in the same structural way and high confidence in precision and
recall of the chunk retrieval is required.
CTS is well suited when the representation of the desired information varies
slightly and the output of the chunk retrieval is further processed by a human.
In cases where the textual representation of the desired information in the log
is unpredictable or varies greatly, KWS ssems to be the best choice. However, its low precision---it extracts a context of multiple lines around a finding---makes it generally unsuited for automatic on-ward processing and instead requires a human to further inspect and interpret the output chunk.

>>>>

\lstset{language=caml, morekeywords={StartExtraction, RegexPosition, RegexPair,
  EndExtraction}, keywordstyle=\bfseries\color{black}, escapeinside=//}
\begin{figure}[!t]
  \centering
  \begin{lstlisting}[breaklines=true]
StartExtraction(RegexPair("Colon/{\color{Plum}$\circ$}/Line Separator", "ALL CAPS")) in EndExtraction(RegexPair("/{\color{Plum}$\varepsilon$}/", "Line Separator/{\color{Plum}$\circ$}/Line Separator"))
  \end{lstlisting}  
  \caption{Simiplified regular expression produced by PBE when trained
  with examples from \Cref{lst:chunk-example-1,lst:chunk-example-2}}
  \label{lst:prose-program-simplified}
\end{figure}

@@

The results of our empirical comparison study on the chunk retrieval techniques
show that the structural representation of the targeted chunk greatly influences
the performance of the chunk retrieval techinques.
\Cref{lst:chunk-example-1,lst:chunk-e:xample-2} show two exemplary log chunks
from Android/Gradle build logs marked in blue.
Both chunks contain the information on why the
corresponding build failed. When PBE is trained on these two examples it produces
a regular expression similar to \Cref{lst:prose-program-simplified}. The retrieval
starts after a colon followed by a line separator and before a capital letter.
It ends before two line separators, consistent with the two example chunks from
\Cref{lst:chunk-example-1,lst:chunk-example-2}.
This shows, that the characters structuring the text around the chunk are
cruicial for regular expressions to identify the targeted log chunk.
In fact, if the third
example from \Cref{lst:chunk-example-3} with a different structural
representation is added, PBE is not able to syntesize a program and returns
``\texttt{no program found}''.
We express this difference in structural representation through dividing log
chunks into structural categories. The chunks from
\Cref{lst:chunk-example-1,lst:chunk-example-2} are in the same structural
category, while the chunk from \Cref{lst:chunk-example-3} is in a different one.

@@

@@

We recommend PBE for use cases where the desired information is always
represented in the same structural way and high confidence in precision and
recall of the chunk retrieval is required.
CTS is well suited when the representation of the desired information varies
slightly and the output of the chunk retrieval is further processed by a human.
In cases where the textual representation of the desired information in the log
is unpredictable or varies greatly, KWS seems to be the best choice. However,
its low precision---it extracts a context of multiple lines around a
finding---makes it generally unsuited for automatic on-ward processing and
instead requires a human to further inspect and interpret the output chunk.
